Ms. No. PSRM-OA-2019-0126 entitled ``Taking Dyads Seriously''

### 2020-02-14 revisionMemo/rev2.tex
talk about spatial stuff

\begin{enumerate}
	\item The additive and multiplicative effects (AME) model presented in the paper allows for a better treatment of first, second and third order dependencies in the data, and account for unobserved sources of bias in the data. The presentation of the AME estimator is clear, and the simulations provide clear evidence that the model outperforms naive OLS/GLM models fitted to the same data. The paper will be of great interest to the PSRM audience and is likely to have a strong impact on future research in international relations. I do, however, have a few suggestions for revisions that will hopefully strengthen the paper’s contributions.
		We thank the reviewer for their comments and suggestions.
	\item The paper shows that the AME model performs well in comparison to the “oracle” model where all sources of dependencies in the data are accounted for, which is reassuring. Yet this comparison feels incomplete. First, the naive model is clearly misspecified given the underlying data generating process. A large number of dependencies in international relations are linked to geography. What would happen if the dependencies were modeled using spatial econometric techniques?
		CDMG: Flag for discussion. We brainstormed how to fit this into the simulation, but wouldn't simulating a W matrix be a bit arbitrary here?
		Reference papers that have thought about what happens when we get the wrong W
		general gist .. spatial models of dyadic dvs are great if we know how to characterize the diffusion amtrices, but the point of our approach is that we may not know how to actually characterize the ways in which actors are related to one another on some diffusion space.
		citations ... flo ... and others based on something that we had researched in the past
		reference franzesse et al mstar framework as a way to operationalize multiple pathways of diffusion in a spatial econometric approach

>>>>

\begin{enumerate}
	\item The additive and multiplicative effects (AME) model presented in the paper allows for a better treatment of first, second and third order dependencies in the data, and account for unobserved sources of bias in the data. The presentation of the AME estimator is clear, and the simulations provide clear evidence that the model outperforms naive OLS/GLM models fitted to the same data. The paper will be of great interest to the PSRM audience and is likely to have a strong impact on future research in international relations. I do, however, have a few suggestions for revisions that will hopefully strengthen the paper’s contributions.
	\begin{itemize}
		\item \textcolor{blue}{ \emph{
		We thank the reviewer for their comments and suggestions.
		}}
	\end{itemize}
	\item The paper shows that the AME model performs well in comparison to the “oracle” model where all sources of dependencies in the data are accounted for, which is reassuring. Yet this comparison feels incomplete. First, the naive model is clearly misspecified given the underlying data generating process. A large number of dependencies in international relations are linked to geography. What would happen if the dependencies were modeled using spatial econometric techniques?
	\begin{itemize}
		\item \textcolor{blue}{ \emph{
%		CDMG: Flag for discussion. We brainstormed how to fit this into the simulation, but wouldn't simulating a W matrix be a bit arbitrary here?
%		Reference papers that have thought about what happens when we get the wrong W
%		general gist .. spatial models of dyadic dvs are great if we know how to characterize the diffusion amtrices, but the point of our approach is that we may not know how to actually characterize the ways in which actors are related to one another on some diffusion space.
%		reference franzesse et al mstar framework as a way to operationalize multiple pathways of diffusion in a spatial econometric approach
In the appendix, we compare our models approach in simulations to a number of other methods of dealing with dependencies, notably LIST THEM. In the simulation, we do not include a spatial lag model because this would require specifying a spatial dependence pattern. Further, spatial lags are likely to be particularly complex in the cases of dyadic data because we would need an appropriate measure of dyadic similarity (see \citet{plumper:neumayer:2010}).

NOTE TO US: Reading this Q again, do they want us to redo the simulation such that the variance is coming from spatial stuff?
